
\documentclass[10pt,a4paper]{article}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Packages and Theorem Environments

\usepackage{graphicx}
\usepackage{psfrag}
\usepackage{epsf}
\usepackage{amsmath,amsfonts,amssymb,latexsym}
\usepackage{enumitem}
\usepackage{algorithmic}
\usepackage{algorithm}
\usepackage[width=160mm,height=240mm,left=35mm,foot=10mm]{geometry}
\usepackage{xcolor}
\usepackage{url}
\usepackage{hyperref}
\usepackage{tikz}


\renewcommand{\theequation}{\thesection.\arabic{equation}}
\newcommand{\makeTiny}[1]{{\tiny #1}}
\newcommand{\work}{\tiny}
\newcommand{\ignore}[1]{}
\newcommand{\startClaims}{\setcounter{claim}{0}}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{problem}[theorem]{Problem}
\newtheorem{question}[theorem]{Question}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{task}[theorem]{Task}
\newtheorem{claim}{Claim}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{observation}[theorem]{Observation}



\title{MATH 351--004 -- Assignment \#$0$\\
}

\author{Alex Iacob\\
ai9388}

\date{August 26, 2021}

\begin{document}

\maketitle

\begin{center}
{\bf \large Part 2}
\end{center}

\subsection*{Problem 1 - What’s the most interesting thing you learned this summer?}

Over the summer, I learned about databases and how to communicate with them. I worked on a 
semester-long project with two others. For this project, we were given an empty database and
we initially had to populate it with data directly from another database, then create arbitrary
accounts to store this data. Then after we added the data to each of these accounts, we used
database connections in Java to use SQL to get the necessary data used to then later display 
everything. It was a very fun experience learning all of the necessary theories for the project.

\subsection*{Problem 2 - Tell me something you already knew about graphs.}

A graph is a $lot$ more versatile than I was lead to believe prior to entering college. You can
essentially use a graph to map anything that would ever want. Graphs became more notable when learning 
about searching algorithms and how essentially any search algorithm will work on some degree of a graph, 
which is pretty cool.

\subsection*{Problem 3 - What is something you want to learn about graphs this semester?}

I do not have anything in particular that I would like to learn, however, I just hope to get a better
grasp on graphs to help my understanding in Computer Science.

\subsection*{Problem 4 - What is your favorite building?}

My favorite building right now is probably the apartment that is my home. I have lived there
since I was born an only went away because of college. My favorite building on campus at the moment is 
Slaughter Hall mainly because not many people go there, so it is usually quiet and I can work there
undisturbed.



\end{document} 




















